### 2013-11-29 PositionPaper/incremental.tex
no message

Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA derivation computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results. The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process. The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated. 
The following sections describe how this query is computed according to our approach.

>>>>

Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results. The output of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process. The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated. 
The following sections describe how this query is evaluated according to our approach.
